Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-15 ms/SI.Rmd
Add SI environment fig

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "comm_scaled_list",
  "occ_point_data_ferns",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results"
))
```

@@

```{r abundance, width = 7, height = 5}
k <- scales::unit_format(unit = "k", scale = 1e-3, accuracy = 1, sep = "")

>>>>

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "comm_scaled_list",
  "occ_point_data_ferns",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results",
  "japan_shp"
))
```

@@

```{r envir, fig.width = 7, fig.height = 9}

# Restrict sites to only those used in model
# (drops outlier % apomictic site)
biodiv_ferns_for_plotting <-
  biodiv_ferns_spatial %>%
  drop_apo_outlier

# crop high-res map of Japan to spatial div results area
japan <- sf::st_crop(japan_shp, sf::st_bbox(biodiv_ferns_for_plotting))

# Set CRS
japan_crs <- sf::st_crs(japan)
biodiv_ferns_for_plotting <- sf::st_set_crs(biodiv_ferns_for_plotting, japan_crs)

# Define function for plotting environment
plot_env <- function(part, label, var_select, fill_lab = "", labels = ggplot2::waiver()) {
  ggplot() +
    geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
    geom_sf(data = biodiv_ferns_for_plotting, aes(fill = .data[[var_select]]), color = "transparent", alpha = 0.8) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**{part}** {label}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") + 
    labs(fill = fill_lab) +
    scale_fill_scico(palette = "lajolla", labels = labels) +
    scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
    theme_grey(base_size = 10) +
    theme(
      panel.grid.major = element_line(color = "grey60", size = 0.1),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      axis.ticks = element_blank(),
      axis.text = element_text(color = "grey60"),
      axis.title = element_blank(),
      legend.position = "right",
      legend.title = element_markdown()
    )
}

a <- plot_env("A", "Area", "area", "km^2")
b <- plot_env("B", "% apomictic taxa", "percent_apo", labels = function(x) scales::percent(x, accuracy = 1))
c <- plot_env("C", "Precipitation", "precip", "mm")
d <- plot_env("D", "Precip. season.", "precip_season" , "")
e <- plot_env("E", "Temperature", "temp", "°C", function(x) x/10)
f <- plot_env("F", "Temp. season.", "temp_season")

a + b + c + d + e + f + plot_layout(ncol = 2, nrow = 3)

ggsave(result_file(figure("envir"), "pdf"), width = 6, height = 8, units = "in")
```

**`r s_figure("envir")`**. Reproductive mode and environmental data in 0.2 degree grid cells across Japan. **A**, rolling mean area (km^2^) in 1° latitudinal bands.  **B**, % apomictic taxa. **C**, annual precipitation **D**, percipitation seasonality (coefficient of variation).  **E**, mean annual temperature. **F**, temperature seasonality (standard deviation × 100).

```{r abundance, fig.width = 7, fig.height = 5}
k <- scales::unit_format(unit = "k", scale = 1e-3, accuracy = 1, sep = "")

### 2021-07-15 ms/manuscript.Rmd
Add SI environment fig

We used data compiled by @Ebihara2019b, which classifies each fern taxon as sexual, apomictic, mixed (both sexual and apomictic modes known from the same taxon), or unknown. 
We calculated the percentage of apomictic species in each grid cell as the sum of apomictic and mixed taxa divided by total number of taxa.

@@

We downloaded climate data at the 2.5 minute scale from the WorldClim database using the `r func("getData")` function in the R package `r pack("raster")`, and extracted four variables related to our research questions as follows: mean annual temperature (bio1; hereafter "temperature"), temperature seasonality (bio4), annual precipitation (bio12; hereafter "precipitation"), and precipitation seasonality (bio15). 
We identified the intersection of the climate data at the 2.5 minute scale with the 0.2° grid-cells, then calculated the mean of each climatic variable for each 0.2° grid-cell.
We calculated area as rolling mean area (km^2^) across 1 degree latitudinal bands.
This approach reflects the idea that the amount of area with a given climate regime enclosing each grid cell may influence species richness of that cell [@Fahrig2013], and that simply using raw island areas would not be appropriate in this context as there are just four very large islands with many much smaller ones located close by.
The R package `r pack("sf")` was used for GIS analyses.

>>>>

We used data compiled by @Ebihara2019b, which classifies each fern taxon as sexual, apomictic, mixed (both sexual and apomictic modes known from the same taxon), or unknown. 
We calculated the percentage of apomictic species in each grid cell as the sum of apomictic and mixed taxa divided by total number of taxa (`r s_figure("envir")`B).

@@

We downloaded climate data at the 2.5 minute scale from the WorldClim database using the `r func("getData")` function in the R package `r pack("raster")`, and extracted four variables related to our research questions as follows: mean annual temperature (bio1; hereafter "temperature"), temperature seasonality (bio4), annual precipitation (bio12; hereafter "precipitation"), and precipitation seasonality (bio15) (`r s_figure("envir")`). 
We identified the intersection of the climate data at the 2.5 minute scale with the 0.2° grid-cells, then calculated the mean of each climatic variable for each 0.2° grid-cell.
We calculated area as rolling mean area (km^2^) across 1 degree latitudinal bands.
This approach reflects the idea that the amount of area with a given climate regime enclosing each grid cell may influence species richness of that cell [@Fahrig2013], and that simply using raw island areas would not be appropriate in this context as there are just four very large islands with many much smaller ones located close by.
The R package `r pack("sf")` was used for GIS analyses.
